Probing the Deuteron at Very Large Internal Momenta

### 2020-07-21 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/MARKED_PRL/body-rev.tex
updated

over the kinematic bin. The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the Laget PWIA and 

@@

\noindent FSI models but negligible effects on the cross sections were found. The experimental and theoretical reduced cross sections were extracted and are defined as follows:

>>>>

over the kinematic bin. The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the Laget PWIA and FSI models but negligible effects on the cross sections 

@@

\noindent were found. The experimental and theoretical reduced cross sections were extracted and are defined as follows:

### 2020-07-21 MY_PUBLICATIONS/PRL/draft_v5_HCsuggestions/body.tex
updated

\indent Between data and theory, for recoil momenta $p_{\mathrm{r}} \sim 0.55-1.0$ GeV/c, all models exhibit a

@@

behavior (smaller fall-off) that overshadows any possibility of extracting the genuine momentum distributions.\\

>>>>

\indent For recoil momenta $p_{\mathrm{r}} \sim 0.55-1.0$ GeV/c (Figs. \hyperref[fig:fig1]{1(a), 1(b)}), all models exhibit a

@@

behavior (smaller fall-off) that overshadows any possibility of extracting the approximate momentum distributions.\\
